Attack-Tolerance in Structured Networks via Multipath Routing \\ Draft: 2016-02-18

### 2016-02-20 ec-2016/source/paper.tex
Add section:Trust

Source-to-network
\begin{figure}
\centerline{\includegraphics{fig-trust-source}}
\caption{TODO}
\label{fig:trust-source}
\end{figure}

Source-to-destination
\begin{figure}
\centerline{\includegraphics{fig-trust-source-destination}}
\caption{TODO}
\label{fig:trust-source-destionation}
\end{figure}

>>>>

We now propose a decentralized trust model based on weaker transitivity
asumptions than existing web of trust models.
In following sections, we will use this model to utilize network redundancy and
minimize vulnerabilities due to single points of failure.
Our model is based on the assumption of partially-transitive trust.
While this assumption is still idealized, it is a more realistic improvement
on fully-transitive models.

Our model (Figure \ref{fig:trust-source})
is represented as an undirected graph or network,
with nodes representing individual
agents and edges representing direct and mutual trust relationships.
We define a {\em trust radius} $h$ and assume that trust is transitive
up to $h$ hops away.
In other words, the nodes $v$ trusts $w$ if the distance
$d(u,v) < h$.
We call the all such nodes the {\em trusted neighborhood} $T_h(v)$,
and all noes at exactly distance $h$ the {\em trust boundary} $B_h(v)$:
\beq
T_h(v) &=& \left\{ w \mid d(v,w) < h \right\} \\
B_h(v) &=& \left\{ w \mid d(v,w) = h \right\}.
\eeq
We assume that no nodes within the trusted neighborhood can be compromised
by an adversary of $v$.
However, by compromising all nodes in the trust boundary, an adversary can
ensure that all communications leaving the trusted neighborhood are compromised.

Source-to-network
\begin{figure}
\centerline{\includegraphics{fig-trust-source}}
\caption{
Illustration of the {\em partial trust} model.
Edges represent direct, mutual trust relationships.
Alice ($v$) trusts all nodes less than
$h$ hops away---her {\em trusted neighborhood} $T_h(v)$.
Beyond that, the nodes at distance $h$ form her {\em trust boundary} $B_h(v)$.
We assume adversaries are unable to compromise nodes in the trusted neighborhood.
By compromising all nodes in the trust boundary, an adversary can ensure that
all communications leaving Alice's trusted neighborhood are compromised.
}
\label{fig:trust-source}
\end{figure}

Now we consider a source $v$ (Alice) and a destination $w$ (Bob),
shown in Figure \ref{fig-trust-source-desitnation}.
We assume that a message beween Alice and Bob will not be compromised in
either of their trusted neighborhoods.
An adversary could compromise all possible paths between Alice and Bob
by compromising either Alice or Bob's entire trust boundary,
which requires compromising $\min(|T_h(v)|, |T_h(w)|)$ nodes.
In a vertex transitive network, these two trust boundaries will be the same size.
If disjoint paths exist connecting each node in Alice's trust boundary to
a node in Bob's, then the cut size between the two can never be smaller than
$|T_h(v)| = |T_h(v)|$,
so an adversary compromises fewer nodes, they cannot compromise all possible
paths between Alice and Bob.

\begin{figure}
\centerline{\includegraphics{fig-trust-source-destination}}
\caption{
Partial trust model with sender (Alice) and receiver (Bob).
If disjoint paths exist connecting each node in Alice's trust boundary to
a node in Bob's,
than an adversary needs to compromise at least $|T_h(v)|$ nodes to
compromise all possible paths between Alice and Bob.
}
\label{fig:trust-source-destionation}
\end{figure}
